### 2021-07-05 rad-icfp-2021/correctness.tex
fixing array notation

\begin{definition}[$\ConcatT$]
Let $\ConcatT$ be the syntactic Cartesian concategory whose types are those of Target and 
with primitives given by 
$op1: \reals \to \reals$, 
$op2: \reals,\reals \to \reals$, 
$map2_{x,y.e}: \Array{\reals},\Array{\reals}\to \Array{\reals}$, 
$reduce_{x,y.e1;e2}: \Array{\reals} \to \Array{\reals}$, 
$J^Top1: \reals \to \reals$, 
$J^Top2: \reals \to \reals, \reals$, 
$J^Tmap2_{x,y.e}: \Array{\reals} \to \Array{\reals}, \Array{\reals}$, 
$J^Treduce_{x,y.e1;e2}: \Array{\reals} \to \Array{\reals}$, 
\MH{not too sure, should I say what a Cartesian concat is? do I need $J^Tproj$?}
\end{definition}

>>>>

\begin{definition}[$\ConcatT$]
Let $\ConcatT$ be the syntactic Cartesian concategory whose types are those of Target and 
with primitives given by 
$op1: \reals \to \reals$, 
$op2: \reals,\reals \to \reals$, 
$map2_{x,y.e}: \Array{\reals}{n},\Array{\reals}{n}\to \Array{\reals}{n}$, 
$reduce_{x,y.e1;e2}: \Array{\reals}{n} \to \Array{\reals}{n}$, 
$J^Top1: \reals \to \reals$, 
$J^Top2: \reals \to \reals, \reals$, 
$J^Tmap2_{x,y.e}: \Array{\reals}{n} \to \Array{\reals}{n}, \Array{\reals}{n}$, 
$J^Treduce_{x,y.e1;e2}: \Array{\reals}{n} \to \Array{\reals}{n}$, 
\MH{not too sure, should I say what a Cartesian concat is? do I need $J^Tproj$?}
\end{definition}
